The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-21 ms.Rmd
incorporating new maxlike modules and removing excess text

All of these have now been uploaded to the ZOON modules repository (under the names `CarolinaWrenPO`, `CarolinaWrenPA`, and `MaxLike`), though we display the code required for the module `CarolinaWrenPO` here as an illustration of the minimal overhead required in writing `zoon` software modules:

```{r carolinamodule, eval = FALSE}
CarolinaWrenPO <- function() {

  # load maxlike package (installing if it isn't in the library)
  zoon::GetPackage('maxlike')

  # load the dataset from the maxlike package
  data(carw, envir = environment())
  occ <- na.omit(carw.data$pa.data)

  # keep only presence records
  occ <- occ[occ$y == 1, ]

  # build the occurrence dataset and return
  data.frame(longitude = occ$Lon,
             latitude = occ$Lat,
             value = occ$y,
             type = 'presence'),
             fold = 1)

}
```

This function meets the requirements of an *occurrence* module; providing as output a dataframe with the required columns and datatypes.

We can run automated checks on this module

@@

```{r merowpreamblel, eval = TRUE, echo = FALSE}

# Load the data into the global environment
data(carw, envir = environment(), package = 'maxlike')

rl <- lapply(carw.data$raster.data, function(x) {
   m <- matrix(x, nrow=carw.data$dim[1], ncol=carw.data$dim[2],
               byrow=TRUE)
   r <- raster(m)
   extent(r) <- c(-124.83, -66.67, 24.61, 49.41)
   r
})

# Stack and name them
CarolinaRasters <- stack(rl[[1]], rl[[2]], rl[[3]], rl[[4]], rl[[5]], rl[[6]])
names(CarolinaRasters) <- names(carw.data$raster.data)

```{r merowWorkingCopy, eval = FALSE}

Merow_Silander <- workflow(
    occurrence = Chain(LocalOccurrenceData(occurrenceType = 'presence'),
                       LocalOccurrenceData(occurrenceType = 'presence/absence',
                                           externalValidation = TRUE)),
     covariate = LocalRaster('CarolinaRasters'),
       process = Chain(Transform(trans = 'square',
                                 replace = FALSE), 
                       Background(n = 10000)),
         model = list(LogisticRegression, MaxEnt, MaxLike),
        output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap))

@@

Merow_Silander <- workflow(
    occurrence = Chain(LocalOccurrenceData(occurrenceType = 'presence' ),
                       LocalOccurrenceData(occurrenceType = 'presence/absence', externalValidation = TRUE)),
     covariate = LocalRasterData('CarolinaRasters'),
       process = Chain(Transform(trans = 'square', replace = FALSE), 
                       Background(n = 10000)),
         model = list(LogisticRegression, MaxEnt, MaxLike),
        output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap, Coefficients)
```

>>>>

All of these have now been uploaded to the ZOON modules repository under the names `CarolinaWrenPO`, `CarolinaWrenPA`, `CarolinaWrenRasters` and `MaxLike`.

@@

```{r merowworkflow, eval = TRUE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Background(n = 10000),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PrintMap))
```

@@

Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Chain(Transform(trans = 'square',
                                 replace = FALSE), 
                       Background(n = 10000)),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap, Coefficients))
```
